Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
synthesize -> synthesise

There has been previous work to formally verify uncertain linear systems
stability in digital controllers with considerations to the implementation
aspects ({\it i.e.}, fixed-point arithmetic and word-length)~\cite{Bessa16}. 
In particular, Bessa {\it et al.} consider finite-word length (FWL) effects
over digital controllers and also parameter uncertainties in the context of
verifying the (so-called) robust non-fragile
stability~\cite{bhattacharyya97}.  However, the authors do not consider the
compete range of approximations, related to time discretisation, and
quantisation effects.  As a result, the stability verification method
proposed by Bessa {\it et al.} is incomplete, given that false alarms can be
produced due to quantisation effects.  Additionally, the authors do not
find a parametric solution for a digital controller given as a continuous
plant specification, in order to synthesize the controller implementation.

@@

The digital controllers synthesized in this paper are typically used in closed loops with continuous (and physical) plants. Thus, the proposed approach has to consider dynamics of continuous parts of system ({\it e.g.}, plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the synthesized controller has to consider the issues related to the hybrid systems studies.

@@

Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
domain,
%
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
%
However, given a real plant $\hat{G}(z)$, and a discretising function
\begin{align}
\small
\label{FWL_tf}
&f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x) \\
&FWL_b[P \in \mathcal{P}] = \tilde P \in \mathcal{P}^{n}\langle I_b,F_b \rangle : c_i \in P \wedge \tilde c_i \in \tilde P=f_b(c_i)  \nonumber
\end{align}
we calculate $\tilde G(z)=FWL_b(\hat{G}(z))$
\begin{align}
% \label{digital_controller_tf}
% \tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
% &= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
&=\hat{G}(z)+\Delta{G}_b(z)=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
\end{align}
where $\Delta_b\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
and $\Delta{G}_b(z)$ represents the plant uncertainty caused by
the rounding off effect.  We may encompass all the uncertainty as
$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  % Since this value is
% nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
% denoted by $\mathfrak{G}(z)$.

@@

Using the closed-loop control system benchmarks described in Section~\ref{experimental-setup}, 
the experimental evaluation of the present approach aims to answer two research questions:
%
\begin{enumerate}
	\item RQ1 \textbf{(sanity check)} which results does our CEGIS approach to FWL controller synthesis 
	obtain upon synthesizing/verifying benchmarks that compose the specified suite?
  \item RQ2 \textbf{(performance)} does the CEGIS approach provide a feasible solution in reasonable time
	considering robust stability of FWL digital controllers?	
\end{enumerate}

>>>>

There has been previous work to formally verify uncertain linear systems
stability in digital controllers with considerations to the implementation
aspects ({\it i.e.}, fixed-point arithmetic and word-length)~\cite{Bessa16}. 
In particular, Bessa {\it et al.} consider finite-word length (FWL) effects
over digital controllers and also parameter uncertainties in the context of
verifying the (so-called) robust non-fragile
stability~\cite{bhattacharyya97}.  However, the authors do not consider the
compete range of approximations, related to time discretisation, and
quantisation effects.  As a result, the stability verification method
proposed by Bessa {\it et al.} is incomplete, given that false alarms can be
produced due to quantisation effects.  Additionally, the authors do not
find a parametric solution for a digital controller given as a continuous
plant specification, in order to synthesise the controller implementation.

@@

The digital controllers synthesised in this paper are typically used in closed loops with continuous (and physical) plants. Thus, the proposed approach has to consider dynamics of continuous parts of system ({\it e.g.}, plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the synthesised controller has to consider the issues related to the hybrid systems studies.

@@

Since the controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
domain,
%
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
%
However, given a real plant $\hat{G}(z)$, and a discretising function
\begin{align}
\small
\label{FWL_tf}
&f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x) \\
&FWL_b[P \in \mathcal{P}] = \tilde P \in \mathcal{P}^{n}\langle I_b,F_b \rangle : c_i \in P \wedge \tilde c_i \in \tilde P=f_b(c_i)  \nonumber
\end{align}
we calculate $\tilde G(z)=FWL_b(\hat{G}(z))$
\begin{align}
% \label{digital_controller_tf}
% \tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
% &= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
&=\hat{G}(z)+\Delta{G}_b(z)=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
\end{align}
where $\Delta_b\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
and $\Delta{G}_b(z)$ represents the plant uncertainty caused by
the rounding off effect.  We may encompass all the uncertainty as
$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  % Since this value is
% nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
% denoted by $\mathfrak{G}(z)$.

@@

Using the closed-loop control system benchmarks described in Section~\ref{experimental-setup}, 
the experimental evaluation of the present approach aims to answer two research questions:
%
\begin{enumerate}
	\item RQ1 \textbf{(sanity check)} which results does our CEGIS approach to FWL controller synthesis 
	obtain upon synthesising/verifying benchmarks that compose the specified suite?
  \item RQ2 \textbf{(performance)} does the CEGIS approach provide a feasible solution in reasonable time
	considering robust stability of FWL digital controllers?	
\end{enumerate}
